### 2024-06-07 manuscript.Rmd
added images

Some default behavior of the package can be changed via R `options()`. The package defines the following options:
- reproducibleRchunks.digits. This is the number of digits for rounding of numbers and controls the numeric precision of the reproducibility checks. By default, this is $8$.

>>>>

Some default behavior of the package can be changed via R `options()`. The package defines the following options:
- reproducibleRchunks.digits: This is the number of digits for rounding of numbers and controls the numeric precision of the reproducibility checks. By default, this is $8$.
- reproducibleRchunks.filetype: By default this is 'json' 
- reproducibleRchunks.hashing:
- reproducibleRchunks.hashing_algorithm: This is the hashing algorithm, which is used to generate fingerprints of variable contents. By default, the `digest` package is used
- reproducibleRchunks.templates:
